Milk intake and risk of mortality risk

### 2020-06-12 Paperfolder/Paperfolder.Rmd
updated change the bib file

---
title: Milk intake and risk of mortality risk 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: mybibfile.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

>>>>

---
title: Milk intake and risk of mortality risk 
author:
  - name: Chaochen Wang
    affil: 1,*
    orcid: 0000-0001-5533-1497
  - name: Hiroshi Yatsuya
    affil: 2 
    orcid: 0000-0002-6220-9251
  - name: Yingsong Lin
    affil: 1
    orcid: 0000-0003-0214-3649
  - name: Tae Sasakabe 
    affil: 1 
    orcid: 0000-0002-7417-5693
  - name: Sayo Kawai
    affil: 1
    orcid: 0000-0002-5156-4880
  - name: Shogo Kikuchi
    affil: 1
    orcid: 0000-0001-9499-9668
  - name: Hiroyasu Iso
    affil: 3
    orcid: 0000-0002-9241-7289 
  - name: Akiko Tamakoshi
    affil: 4
    orcid: 0000-0002-9761-3879 
affiliation:
  - num: 1
    address: |
      Department of Public Health, Aichi Medical University School of Medicine, Nagakute, Japan
#    email: chaochen@wangcc.me
  - num: 2
    address: |
      Departmet of Public Health, Fujita Health University School of Medicine, Toyoake, Japan
  - num: 3
    address: |
      Public Health, Department of Social Medicine, Osaka University Graduate School of Medicine, Osaka, Japan
  - num: 4
    address: |
      Department of Public Health, Faculty of Medicine, Hokkaido University, Sapporo, Japan
#    email: yatsuya@gmail.com
# firstnote to eighthnote
# firstnote: |
#   Current address: Updated affiliation
# secondnote: |
#   These authors contributed equally to this work.
correspondence: |
  Email.: chaochen@wangcc.me; Tel.: +81-561-62-3311. Department of Public Health, Aichi Medical University School of Medicine, 1-1 Yazakokarimata, Nagakute, Aichi, 480-1195, Japan (C.W.)
journal: nutrients
type: article
status: submit
bibliography: milk.bib
# appendix: appendix.tex
# simplesummary: |
#  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.''
conflictsofinterest: |
  The authors declare no conflict of interest. The founding sponsors had no role in the design of the study; in the collection, analyses, or interpretation of data; in the writing of the manuscript, an in the decision to publish the results.
# sampleavailability: |
#   Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: JACC
    long: Japan Collaborative Cohort 
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---
